Figures from: Vertebrate host availability and the thermal properties of mosquito-borne parasite transmission

### 2023-06-07 manuscript-figures.Rmd
update R0 values

## Configure data frame for plotting
R0_df <- data.R0 %>%
  select(system_ID, system_label, Temperature, sigmaH, KH, median) %>%
  rename(R0 = median) %>%
  # Consider only 3 values of KH (on a log10-scale)
  filter(KH %in% c(1E-1, unique(data.R0$KH)[7], unique(data.R0$KH)[10])) %>% # !!! temporary. recalculate R0 with 1e-1, 1e0, 1e1
  # Choose a limited range of sigmaH values
  filter(sigmaH > 10^0.5) %>%
  # Group by plotting variables
  group_by(system_ID, KH, sigmaH) %>%
  # Calculate Topt (which.max requires grouping)
  mutate(Topt = `Temperature`[which.max(R0)]) %>%
  as_tibble() %>%
  arrange(system_ID, sigmaH, Temperature)

>>>>

## Configure data frame for plotting
R0_df <- data.R0 %>%
  select(system_ID, system_label, Temperature, sigmaH, KH, median) %>%
  rename(R0 = median) %>%
  # Consider only 3 values of KH (on a log10-scale)
  # filter(KH %in% c(1E-1, unique(data.R0$KH)[7], unique(data.R0$KH)[10])) %>% # !!! temporary. recalculate R0 with 1e-1, 1e0, 1e1
  # Choose a limited range of sigmaH values
  filter(sigmaH > 10^0.5) %>%
  # Group by plotting variables
  group_by(system_ID, KH, sigmaH) %>%
  # Calculate Topt (which.max requires grouping)
  mutate(Topt = `Temperature`[which.max(R0)]) %>%
  as_tibble() %>%
  arrange(system_ID, sigmaH, Temperature)
